Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
Bens Kommentare

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=red!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\bz}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}

@@

\emph{Context-specific exclusive or of property groups} (\emph{R-11}) is a constraint type which can be formulated by a high-level constraint language. Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups. \emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:\ke{Wo kommt das constraint her? In SKOS gilt das nicht generell.}
%(\emph{error}).

@@

85\% of the QB constraints are \emph{error} constraints.
More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}
For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
\end{hyp}

@@

\begin{enumerate}
\item
\emph{Data quality can be significantly improved when suitable constraint languages are developed which enable to define 
constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way. Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}}
\item
\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}  
\item
\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations. This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
\item
\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
\end{enumerate}

>>>>

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=red!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\bz}[1]{\todo[size=\small, color=blue!40]{\textbf{Ben:} #1}}

@@

\emph{Context-specific exclusive or of property groups} (\emph{R-11}) is a constraint type which can be formulated by a high-level constraint language. Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups. \emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:\ke{Wo kommt das constraint her? In SKOS gilt das nicht generell.}\bz{Wenn das Constraint keinen SKOS-Ursprung hat, sollten wir ein anderes Beispiel in dem Satz nennen.}
%(\emph{error}).

@@

85\% of the QB constraints are \emph{error} constraints.
More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
%Constraints are serious when they violate the integrity of vocabularies.
%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
%which is not the case or newly-developed vocabularies.
\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
\end{hyp}

@@

\begin{enumerate}
\item
\emph{Data quality can be significantly improved when suitable constraint languages are developed which enable to define 
constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way. Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}\bz{Thomas, meinst du: the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only specified using SPARQL.}}
\item
\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}  
\item
\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations. This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
\item
\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
\end{enumerate}
